full title

### 2020-11-17 paper/pldi21/related.tex
Minor change in related.tex
Added dynamic determinacy analysis in related work.

The most related previous work is the combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.  They
proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach have several
limitations compared to the dynamic shortcut.  First, they syntactically divides
a given program to \textit{applications} parts for static analysis and
\textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switching between static and dynamic and even impossible to perform both
of static and dynamic analysis to the same program part in different contexts.
Besides, they introduced \textit{mostly-concrete interpretation} similar with
our sealed symbolic execution.  However, it supports only a special
\textit{unknown} value that represents any possible value.  Thus, it cannot
preserves the precision of complex abstract domains~\cite{revisit-recency,
regex, weaklySPE} frequently used in JavaScript static analysis.  On the other
hand, the sealed symbolic execution automatically detects whether the abstract
semantics for abstract values.  Finally, \concerto preserves the soundness when
the program satisfies the \textit{state separation hypothesis}.  They assume
that states of application and framework parts do not interrogated or
manipulated by each other.  While it is reasonable for static analysis of Java
applications using external libraries, the assumption is not satisfied for
JavaScript programs in general.  Unlike their approach, our approach does not
have any assumption between static and dynamic analysis parts.

@@

\paragraph{Pruning Analysis Scopes}
Another approach to utilize dynamic analysis for JavaScript static analysis is
to prune the scope of analysis.  \citet{blended} introduced \textit{blended
taint analysis} that specializes JavaScript dynamic language features such as
dynamic code generation (e.g. \jscode{eval}) or variadic function calls.  They
first performs dynamic analysis to collect traces with concrete values used in
dynamic language features and restrict the semantics of features based on the
collected traces during static analysis.  \citet{battles, eha} utilizes three
different points to reduce analysis scopes: initial states, dynamically loaded
files, and event handlers.  They dumped the initial states from a specific web
browser to focus on analyzing the behaviors of web browsers running on the
browser.  Then, they collected paths of dynamically loaded files via concrete
executions and utilized the path information in static analysis.  For event
handlers, they intentionally analyzed partial execution flows using concrete
user events.  They collected concrete states for each entry of event handler
during dynamic analysis, merged them to a single abstract state, and analyzed
the event handler with the abstract state.  Unfortunately, all of them does not
preserve soundness of static analysis unlike the dynamic shortcut.

>>>>

The most related previous work is the combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.  They
proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach have several
limitations compared to the dynamic shortcut.  First, they syntactically divides
a given program to \textit{applications} parts for static analysis and
\textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switching between static and dynamic and even impossible to perform both
of static and dynamic analysis to the same program part in different contexts.
Besides, they introduced \textit{mostly-concrete interpretation} similar with
our sealed symbolic execution.  However, it supports only a special
\textit{unknown} value that represents any possible value.  Thus, it cannot
preserves the precision of complex abstract domains~\cite{revisit-recency,
regex, weaklySPE} frequently used in JavaScript static analysis.  On the other
hand, the sealed symbolic execution automatically detects whether the abstract
semantics are required for abstract values.  Finally, \concerto preserves the
soundness when the program satisfies the \textit{state separation hypothesis}.
They assume that states of application and framework parts do not interrogated
or manipulated by each other.  While it is reasonable for static analysis of
Java applications using external libraries, the assumption is not satisfied for
JavaScript programs in general.  Unlike their approach, our approach does not
have any assumption between static and dynamic analysis parts.

@@

\paragraph{Pruning Analysis Scopes}
Another approach to utilize dynamic analysis for JavaScript static analysis is
to prune the scope of analysis.  \citet{determinacy} proposed dynamic
determinacy analysis that infer determinacy facts via concrete executions that a
variable or expression at a given location holds the same value in all possible
execution of the program.  They specialized target source codes with determinacy
facts so that static analyses could benefit from eliminations of dynamic code
generation (e.g. \jscode{eval}) and constant property names.  \citet{blended}
introduced \textit{blended taint analysis} that specializes JavaScript dynamic
language features such as dynamic code generation or variadic function calls.
They first performs dynamic analysis to collect traces with concrete values used
in dynamic language features and restrict the semantics of features based on the
collected traces during static analysis.  \citet{battles, eha} utilizes three
different points to reduce analysis scopes: initial states, dynamically loaded
files, and event handlers.  They dumped the initial states from a specific web
browser to focus on analyzing the behaviors of web browsers running on the
browser.  Then, they collected paths of dynamically loaded files via concrete
executions and utilized the path information in static analysis.  For event
handlers, they intentionally analyzed partial execution flows using concrete
user events.  They collected concrete states for each entry of event handler
during dynamic analysis, merged them to a single abstract state, and analyzed
the event handler with the abstract state.  Unfortunately, all of them does not
preserve soundness of static analysis unlike the dynamic shortcut.
